---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# obrr

<!-- badges: start -->
<!-- badges: end -->

The goal of `obrr` is to make it easy to retrieve time series of the latest [OBR forecasts](https://obr.uk/forecasts-in-depth/the-economy-forecast/).

## Installation

You can install the package from GitHub with:

```{r, include = TRUE, eval = FALSE}
# install.packages("devtools")
devtools::install_github("l-hodge/obrr")
```

## Example

The following will retrieve a time series of CPI and RPI inflation, including projections from the OBR. 

```{r}
library(obrr)

# Wide
obr_annual(c("CPI", "RPI"), long = FALSE)

# Long
obr_annual(c("CPI", "RPI"), long = TRUE)

```

### Which time series indicators are available? 

You can use `obr_meta()` to display available time series - id, title and units.

```{r, include = FALSE, eval = TRUE}
library(dplyr)
```

```{r, results = "asis", eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE}
obr_meta() %>%
    knitr::kable()
```
